---
title: "Mercury vapour pressure"
author: "Remko Logemann"
date: "February 20, 2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App weblocation

This pitch belongs to the mercury vapour app at: 

https://boe22.shinyapps.io/Week4/

## Dataset

It is based on the mercury vapour dataset of R: 
```{r, echo=TRUE}
plot(pressure)
```

Where the pressure can be approximated by a linear function for low temperatures. 

This the temperature threshold can be configured in the app. 

## Low temperatures

For low temperatures the temperature is approximated by: 

```{r, echo = TRUE}
Model1 <- lm(pressure ~ temperature, data = pressure[pressure$temperature<=100,])
# Get fit values
Model1Pred <- data.frame(temperature = c(pressure[pressure$temperature<=100,'temperature'],100))
Model1Pred[,'pressure'] <- predict(Model1, newdata = Model1Pred)

 plot(pressure$temperature, pressure$pressure, xlab = "Temperature (deg C)", ylab = "Pressure (mm of Hg)")
lines(Model1Pred$temperature, Model1Pred$pressure, col = "red")
abline(v=100, col="blue")
```

## High temperatures

For high temperatures the pressure is approximated by an exponential function:

```{r, echo = TRUE}
Model2 <- lm(log(pressure) ~ log(temperature), data = pressure[pressure$temperature>100,])
 
Model2Pred <- data.frame(temperature = c(100,pressure[pressure$temperature>100,'temperature']))
Model2Pred[,'pressure'] <- Model2Pred[,'temperature']^Model2$coefficients[2]*exp(Model2$coefficients[1])

plot(pressure$temperature, pressure$pressure, xlab = "Temperature (deg C)", ylab = "Pressure (mm of Hg)")
lines(Model2Pred$temperature, Model2Pred$pressure, col = "green")
abline(v=100, col="blue")
```

